%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

\vspace*{-1.5mm}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Instructor}
    {KOLT Python Certificate Program}
    {Koç University, İstanbul, Turkey}
    {Feb. 2019 - PRESENT}
    {
      \begin{cvitems}
        \item {Teaching programming with Python to 20 undergraduate students from different backgrounds as a part of certificate program.}
        \item {Prepared lecture slides, examples, assignments, contests and created course website.}
      \end{cvitems}
    }

  \cventry
    {Section Leader}% Job title
    {COMP 130/131, Introduction to Programming}% Organization
    {Koç University, İstanbul, Turkey}
    {Sep. 2017 - Dec. 2018}
    {
      \begin{cvitems}
        \item {Prepared homework assignments and conducted programming sections for the introductory programming course (Java).}
      \end{cvitems}
    }


  \cventry
    {Researcher for <Head Mounted AR Devices \& Usage of AR in Archaeological Sites and Museums >}% Job title
     {Undergraduate Research, Optical Microsystems Laboratory(Prof. Hakan Ürey)}% Organization
    {Koç University, İstanbul, Turkey}
    {July 2017 - June 2018}
    {
      \begin{cvitems} 
        \item {Using Unity and Vuforia, developed marker based AR application that recognizes a stelai and illustrates possible original colors in real time.}
	      \item {Worked with pupil labs gaze tracking device and developed an Hololens application named HoloGallery that can show historical images.}
      \end{cvitems} 
    }

%---------------------------------------------------------
\end{cventries}
