%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}

\vspace*{-1.5mm}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  % \cventry
  %   {Participant} % Affiliation/role
  %   {inzva Algorithm Competition Programme 2018-2019} % Organization/group
  %   {İstanbul, Turkey} % Location
  %   {Sep. 2018 - PRESENT} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of experience/contributions/knowledge
  %       \item {Includes lectures, contests, problem-solving sessions focused on algorithms and competitive programming.}
  %     \end{cvitems}
  %   }

  \cventry
    {Instructor}
    {CS 101: Merhaba, Dünya! (Hello, world!)}
    {İstanbul, Turkey}
    {Aug. 2020 - PRESENT}
    {
      \begin{cvitems}
        \item {Volunteer at 8-week online program aiming to provide Turkish high school students with fundamental programming skills.}
      \end{cvitems}
    }


  \cventry
    {Founder \& Instructor}
    {KOLT Python Certificate Program}
    {Koç University, İstanbul, Turkey}
    {Feb. 2019 - Jun. 2020}
    {
      \begin{cvitems}
        \item {Created a certificate program that aims to teach basics of computer science to students from nontechnical majors using Python.}
        \item {Prepared lecture slides, examples, assignments, and created \href{https://koltpython.github.io}{the course website}. Managed a team of 8 volunteers.}
      \end{cvitems}
    }

    \cventry
    {Section Leader}% Job title
    {CSBridge (Stanford University - Koç University)} % Organization
    {Koç University, İstanbul, Turkey}
    {Summer 2018, 2019 \& 2020} 
    {
      \begin{cvitems}
        \item{CSBridge aims to give rising high school juniors, especially girls, their first experiences in coding using the curriculum of Stanford's CS106A class.} 	             
        \item{Conducted problem sessions, helped students during lab hours and gave feedback to their daily programming assignments on Java.}
      \end{cvitems}
    }

    \cventry
    {Section Leader}% Job title
    {COMP 130/131, Introduction to Programming}% Organization
    {Koç University, İstanbul, Turkey}
    {Sep. 2017 - Dec. 2018}
    {
      \begin{cvitems}
        \item {Prepared homework assignments and conducted programming sections for the introductory programming course (Java).}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Member \& Computer Society Project Leader at 2017 \& IEEEXtreme 11.0 Student Ambassador}
  %   {IEEE Koç University Student Branch}
  %   {İstanbul, Turkey}
  %   {Sep. 2016 - May 2018}
  %   {
  %     \begin{cvitems}
  %       \item {Worked in the organization of entrepreneurship and career events, prepared programming questions for weekly Python meetings.}
  %       \item {Promoted IEEEXtreme on our campus as student ambassador .}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
