%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

\vspace*{-1.5mm}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \project
    {\href{http://corpexx.com}{corpexx}} % Organization
    {Dec. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems}
        %\item {corpexx is an intelligent recruitment platform powered by machine learning. Using ML corpexx gets to know its users and secretly recognizes their skill levels based on their past experiences and activity. corpexx uses this information to make personal job recommendations to users.}
        %\item {Using this understanding of our users’ skill levels, corpexx allow companies to set threshold skill levels to filter irrelevant applications and increases recruiters’ efficiency by showing applicants’ most relevant experiences first based on specifications of job post.}
        %\item {With its multistage application process, corpexx allows companies to stress the key skills, and aims to solve the uninformed applicant problem.}
        \item {corpexx is an online recruitment platform that aims to make personal job recommendations based on skill levels of the user, filter unqualified applicants by allowing companies to set threshold skill levels for a job post, and increase recruiter efficiency by showing most relevant experiences of applicants first.}
        \item {Currently developing a PWA using Angular, and backend with .NET Core and PostgreSQL.}
      \end{cvitems}
    }

  \project
    {\href{http://prolandfarming.com}{Proland}} % Organization
    {Mar. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems}
        \item {Proland is a machine learning solution to help farmers choose the best product for them using only a mobile application. It uses last years' crop specific harvest data and monthly weather conditions such us temperature, wind and precipitation to give yield estimates for crops.}
        \item {Competed in Imagine Cup, one of the biggest student technology competitions, and qualified for the World Finals as one of the top 50 teams.}
        \item {Used Python to extract weather data, created a cross platform application using Xamarin.Forms, implemented our backend using Firebase.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
